\section{Bottom Line}

\subsection{Conclusion}
The journey of developing the URL-Archiver has been a mix of unexpected challenges and rewarding experiences.
Initially assumed to be straightforward, the project revealed its complexity as we delved deeper.
This experience highlighted the importance of effective team communication, a critical factor in overcoming the unforeseen challenges of the project.
Reflecting on our approach, establishing a more robust project structure from the beginning would have been beneficial.
Despite these challenges, the project was rewarding and a great learning experience.

One of the key takeaways was the value of practical experience with Git.
This tool not only enhanced our collaborative efforts but also contributed to our personal skill development.
Remarkably, the URL-Archiver stands as our first project built entirely from scratch, marking a significant milestone in our journey as developers.

We firmly believe that the URL-Archiver has the potential to be a valuable asset to its users.
By significantly reducing the time and effort required for extracting and archiving URLs, the application promises an increase in productivity for its users.
This improvement is not just theoretical; it's a practical solution addressing a real need in the digital world. Insights into the complexities of web archiving, as discussed in the summary of 'To Re-experience the Web: A Framework for the
Transformation and Replay of Archived Web Pages' \cite{berlin2023reexperience} in Appendix \ref{app:summary_article}, further emphasize the relevance and potential of our project.

In conclusion, while the project journey had its ups and downs, the collective learning and the potential impact of the URL-Archiver make it a fulfilling experience.
We are optimistic about its utility and look forward to seeing its adoption and evolution in the professional world.
\clearpage
\subsection{Productivity Increase Calculation}
This section calculates the estimated productivity increase for users of our URL-Archiver software.
The calculation factors include task duration without and with the software, the resulting time economy, cost per time unit, and overall cost economy.

\subsubsection{Assumptions}
The following assumptions were made for our calculations:
\begin{itemize}
    \item The file contains 60 URLs.
    \item Without URL-Archiver, manually finding and copying each URL takes approximately 12 seconds.
    \item The URL-Archiver takes an average of 2 seconds to find all URLs in a file.
    \item Archiving one URL using Wayback Machine manually takes 60 seconds.
    \item Archiving one URL using Archive Today manually takes 90 seconds.
    \item With URL-Archiver, initiating the archiving process for one URL in Wayback Machine takes 10 seconds. The actual archiving in the background takes in average 30 seconds.
    \item Archiving one URL using Archive Today remains at 90 seconds even with the URL-Archiver.
    \item The average hourly wage for a professional in Switzerland is CHF 40.
    \item Parallel archiving with Wayback Machine allows for multiple URLs to be archived concurrently, reducing the total time significantly.
\end{itemize}

\subsubsection{Wayback Machine Analysis}
\textbf{Without URL-Archiver:}
\begin{align*}
    \text{Task duration without SW} &= \text{URL extraction} + \text{URL archiving} \\
    &= (60 \times 12\, \text{seconds}) + (60 \times 60\, \text{seconds}) \\
    &= 720\, \text{seconds} + 3600\, \text{seconds} \\
    &= 4320\, \text{seconds (72 minutes)}
\end{align*}

\textbf{With URL-Archiver:}
\begin{align*}
    \text{Task duration with SW} &= \text{URL extraction} + \text{URL archiving} \\
    &= 2\, \text{seconds} + (60 \times 40\, \text{seconds}) \\
    &= 2\, \text{seconds} + 2400\, \text{seconds} \\
    &= 2402\, \text{seconds (40 minutes)}
\end{align*}

\textbf{Productivity Increase:}
\begin{align*}
    \text{Task duration economy} &= 72 - 40 = 32\, \text{minutes} \\
    \text{Cost per time unit} &= \frac{40\, \text{CHF}}{60\, \text{minutes}} \\
    \text{Cost economy} &= 32 \times \left( \frac{40\, \text{CHF}}{60} \right) = 21.33\, \text{CHF per document}
\end{align*}

\subsubsection{Archive Today Analysis}
\textbf{Without URL-Archiver:}
\begin{align*}
    \text{Task duration without SW} &= \text{URL extraction} + \text{URL archiving} \\
    &= (60 \times 12\, \text{seconds}) + (60 \times 90\, \text{seconds}) \\
    &= 720\, \text{seconds} + 5400\, \text{seconds} \\
    &= 6120\, \text{seconds (102 minutes)}
\end{align*}

\textbf{With URL-Archiver:}
\begin{align*}
    \text{Task duration with SW} &= \text{URL extraction} + \text{URL archiving} \\
    &= 2\, \text{seconds} + (60 \times 90\, \text{seconds}) \\
    &= 2\, \text{seconds} + 5400\, \text{seconds} \\
    &= 5402\, \text{seconds (90 minutes)}
\end{align*}

\textbf{Productivity Increase:}
\begin{align*}
    \text{Task duration economy} &= 102 - 90 = 12\, \text{minutes} \\
    \text{Cost per time unit} &= \frac{40\, \text{CHF}}{60\, \text{minutes}} \\
    \text{Cost economy} &= 12 \times \left( \frac{40\, \text{CHF}}{60} \right) = 8.00\, \text{CHF per document}
\end{align*}
