\subsubsection{Epic 3: Web Browser Integration}
\textbf{Goal}: Seamlessly open detected URLs, one at a time, in a web browser for user verification, and immediately initiate the archiving process upon user decision.

\begin{enumerate}
    \item \textbf{Sequential URL Preview}
    \begin{itemize}
        \item \textbf{Description}: As a user, I want to preview each detected URL in my default browser sequentially to verify its content.
        \item \textbf{Acceptance Criteria}:
        \begin{itemize}
            \item System opens one URL at a time in the default browser.
            \item Immediately after the URL is displayed, the system presents the user with the option to archive.
        \end{itemize}
    \end{itemize}

    \item \textbf{Immediate Archiving Upon Decision}
    \begin{itemize}
        \item \textbf{Description}: After reviewing a URL in the browser, I want to decide if it should be archived. If I decide to archive, the system should immediately initiate the archiving process.
        \item \textbf{Acceptance Criteria}:
        \begin{itemize}
            \item System provides a prompt to accept or decline the archiving of the displayed URL.
            \item If the user chooses to archive, the system directly begins the archiving process, and the user may need to manually solve captchas.
        \end{itemize}
    \end{itemize}

    \item \textbf{Track Archiving Progress}
    \begin{itemize}
        \item \textbf{Description}: As a user, I want a clear indicator of how many URLs have been displayed, archived, and how many are left to process.
        \item \textbf{Acceptance Criteria}:
        \begin{itemize}
            \item The system displays a counter indicating the number of URLs already shown to the user.
            \item Another counter indicates how many URLs have been chosen for archiving.
            \item Yet another counter shows how many URLs remain to be processed/displayed.
        \end{itemize}
    \end{itemize}

    \item \textbf{Store User Decisions for Reporting}
    \begin{itemize}
        \item \textbf{Description}: As a user, after making a decision about archiving each URL, I want the system to store my choices so that they can be referred to or reported on later.
        \item \textbf{Acceptance Criteria}:
        \begin{itemize}
            \item The system maintains a record of each URL and the user's decision (archived or not archived).
            \item The stored decisions are available for any subsequent reporting needs.
        \end{itemize}
    \end{itemize}

\end{enumerate}