\section{Licensing and Compliance}

\subsection{Licensing Overview}
The project, along with its original source code, is licensed under the permissive and open MIT License. This license aligns with the project's goal of accessibility and ease of use, allowing for free use, modification, distribution, and private use of the software.

\subsection{Compliance with Open Source Licenses}
Although the project itself is licensed under the MIT License, it uses several open-source libraries that are subject to their respective licenses. Please refer to Appendix~\ref{sec:used-libraries} for more information. It is worth noting that this project employs libraries licensed under the Eclipse Public License v2.0 (EPL-2.0), including JUnit Jupiter API.

Using EPL-2.0 licensed libraries in a MIT-licensed project is compliant with open source licensing standards, as long as certain conditions are met.
\begin{enumerate}
    \item \textbf{Attribution and Notices}: The project includes a 'Licenses and Attributions' section in the README file. This section acknowledges the use of open-source libraries, specifying their licenses and providing due credits. Additionally, a `NOTICES.txt` file is included in the project's resources, detailing the open-source components used, their licenses, and where to find the full license texts. This approach is a crucial step to respect and recognize the work of open-source contributors and to maintain transparency about the software's composition.
    \item \textbf{Separation of Licenses}: It is important to clarify that the MIT License applies to the original code developed for this project. In contrast, the libraries used retain their original licenses (EPL-2.0 in the case of JUnit).
    \item \textbf{No Modification of EPL-2.0 Libraries}: This project uses the EPL-2.0 licensed libraries in their unmodified form. Any modification to such libraries would require adherence to the specific terms and conditions of the EPL-2.0.
\end{enumerate}

\subsection{Purpose of Compliance}
Ensuring compliance with the licensing terms of used libraries is not only a legal requirement but also a commitment to the open-source community's ethical standards. It ensures that the project respects the rights and efforts of other developers and contributes to the sustainable and responsible use of open-source software.