\section{Summary of "To Re-experience the Web: A Framework for the Transformation and Replay of Archived Web Pages"}\label{app:summary_article}
The article 'To Re-experience the Web: A Framework for the Transformation and \gls{Replay} of Archived Web Pages' addresses the challenges and solutions related to replaying archived web pages, also known as \glspl{Mementos}\index{Mementos}. The article highlights the following key points:
\begin{enumerate}
	\item \textbf{Expectation from \glspl{WebArchive}\index{Web Archive}:} When replaying a web page from an archive, it is expected that the page will be viewable and function exactly as it did at the time of archival.
	\item \textbf{Necessity of Modifications:} To meet this expectation, web archives modify the page and its embedded resources during replay. This ensures that all resources and links refer to the archive instead of the original server. These modifications are essential for replaying mementos.
	\item \textbf{Variation and Lack of Standard Terminology:} Replaying mementos requires different processes and modifications depending on the web archive used. Standardized terminology to describe these replay methods and necessary modifications is currently lacking.
	\item \textbf{Proposed Framework and Terminology:} The article presents a framework for generating \gls{ClientSideRewriting}\index{Client-Side Rewriting} libraries and establishes terminology for describing replay styles and modifications made by web archives.
	\item \textbf{Effectiveness of Client-Side Rewriter:} A study was conducted to evaluate the use of a generated client-side rewriting library to enhance existing replay systems. The study focused on mementos replayed from the Internet Archive's Wayback Machine, comparing those replayed with and without the client-side rewriter. The results showed that the use of a client-side rewriter reduced the number of requests blocked by the Wayback Machine's \gls{ContentSecurityPolicy} by 87.5\% and increased the total number of requests by 32.8\%.
	\item \textbf{Improved Replay Capability:} The client-side rewriter made it possible to play back mementos that could not previously be played back from the Internet Archive.
	\item \textbf{Implementation in \gls{Wombat} \index{Wombat}:} The article describes several client-side rewriting ideas that have been implemented into Wombat, a client-side URL rewriting system used by the \gls{Webrecorder}, \gls{Pywb}, and Wayback Machine playback systems.
\end{enumerate}